\begin{agradecimentos}

First of all, thank you to my dear family! I couldn't have reached this far without you! To my mom, Gláucia Maria Pacheco Terra, and my dad, Paulo Orlando Martins, who have loved me since and taught me how to be a better person and fight difficulties in life. To my brother Sam Pacheco Martins and sister Élida Pacheco Martins, whom I love so much, despite everything. To my extended family, uncles, aunts, cousins, that are so many to name each, but have seen my potential even when I couldn't see it. Thank you so much! Your faith in me makes me go further than I ever thought I could!

I also want to thank with all the warmth of my heart the friends who have been with me in this journey and helped me through this stressful period of life, either here in Brazil or my dear Canada. Huge thanks to the great Mateus Medeiros Furquim Mendonça and his entire family, Elis, Geovane, and Tiago, for helping me keep my sanity with all the laughs and games, and also for giving me a place to study. I couldn't have done half of this work if you hadn't welcomed and sheltered everytime I needed. To Felipe Pradera Resende, that is the older brother I never had.

Thanks to all instructors that have helped to arrive here. Special thanks to my supervisor, Professor Edson Alves da Costa Junior, who saw potential on a 16 years old boy and never stopped believing in me ever since. To my friend and co-supervisor, Matheus de Sousa Faria, whom I had the pleasure of start working with so many years ago when we were freshmen. Thanks for guiding me through this work!

\end{agradecimentos}
